\chapter[Gaseous Inflows \& Steep Metallicity Profiles]{SDSS-IV/MaNGA: Can impulsive gaseous inflows explain steep oxygen abundance profiles \& anomalously-low-metallicity regions?}
\label{chapter3}

\vfill

\begin{flushright}
    \fixspacing % Single spacing
    \textit{A version of this chapter has been submitted\\
        to the \emph{Astrophysical Journal}} \\ \vspace{1ex}
    Pace, et al.\ 2020, \apj, vol, page \\ \vspace{1ex}
    and is notated P20 throughout this dissertation
\end{flushright}

\vspace*{1in} % Leave a 1-in space at the bottom.

\cleardoublepage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{chabstract}
Gaseous inflows are necessary suppliers of galaxies' star-forming fuel, but are difficult to characterize at the survey scale. We use integral-field spectroscopic measurements of gas-phase metallicity and single-dish radio measurements of total atomic gas mass to estimate the magnitude and frequency of gaseous inflows incident on star-forming galaxies. We reveal a mutual correlation between steep oxygen abundance profiles between $0.25-1.5 ~ R_e$, increased variability of metallicity between $1.25-1.75 ~ R_e$, and elevated HI content at fixed total galaxy stellar mass. Employing a simple but intuitive inflow model, we find that galaxies with total stellar mass less than $10^{10.7} ~ {\rm M_{\odot}}$ have local oxygen abundance profiles consistent with reinvigoration by inflows. Approximately 10-25\% of low-mass galaxies possess signatures of recent accretion, with estimated typical enhancements of approximately 10-90\% in local gas mass surface density. Higher-mass galaxies have limited evidence for such inflows. The large diversity of HI mass implies that inflow-associated gas ought to reside far from the star-forming disk. We therefore propose that a combination of high HI mass, steep metallicity profile between $0.25-1.5 ~ R_e$, and wide metallicity distribution function between $1.25 - 1.75 ~ R_e$ be employed to target possible hosts of inflowing gas for high-resolution radio follow-up.
\end{chabstract}
\cleardoublepage

\graphicspath{{Chapter3-MetDecs/}}

\defcitealias{pace_19a_pca}{MaNGA-PCA Paper \textsc{i}}
\defcitealias{pace_19b_pca}{MaNGA-PCA Paper \textsc{ii}}

\input{Chapter3-MetDecs/chapter3_define.tex}

\input{Chapter3-MetDecs/chapter3_intro.tex}

\input{Chapter3-MetDecs/chapter3_data.tex}

\input{Chapter3-MetDecs/chapter3_gradients.tex}

\input{Chapter3-MetDecs/chapter3_trends.tex}

\input{Chapter3-MetDecs/chapter3_discussion.tex}

\bibliographystyle{thesis.bst}
\bibliography{Chapter3-MetDecs/references}{}